Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
Notation for V-enriched functor category.

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between
hom-monoids in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means
that $F$ preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

>>>>

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between
hom-objects in $V$. Write $\Func{C}{D}_V$ for the category of $V$-enriched functors from $C$ to $D$. In the
specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$ preserves the
additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

If $C$ is $\CMon$-enriched then there is an enriched version of its Yoneda embedding, namely the
$\CMon$-enriched functor $\Yoneda_{\CMon}: \Func{C^\op}{\CMon}$
